Information Retrieval - Submission Report \\Project N.14: Art For Sale

### 2023-12-09 docs/report/submission.tex
feat: report USI logo for cover
Co-authored-by: Filippo Piloni <pilonf@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{hyperref}
\title{Information Retrieval - Submission Report \\Project N.14: Art For Sale}

@@

@@

    \section{Introduction}
    The Information Retrieval course project \textit{"ArtForSale"} aims to be a working prototype of an information
    retrieval system for a specific task: to display for-sale artworks from art selling related websites
    listed in Section \ref{sec:websites}.
    The system has around $\approx 8,500$ indexed documents served through a
    user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}, \ref{sec:ux}.

@@

    \subsection{Features}
    For this project, the following features has been implemented:
    \begin{itemize}
        \item Result presentation
        \item Filtering
        \item Automatic recommendation
    \end{itemize}

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{User Evaluation}

>>>>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{wrapfig}
\title{Information Retrieval - Submission Report \\Project N.14: Art For Sale}

@@

\begin{wrapfigure}{l}{0.25\textwidth}
    \includegraphics[width=0.25\textwidth, trim={0cm 0cm 0cm 7cm}]{USI_logo.png}
\end{wrapfigure}

@@

    \section{Introduction}
    The Information Retrieval course project \textit{"ArtForSale"} aims to be a working prototype of an information
    retrieval system for a specific task: to display for-sale artworks from art selling related websites
    listed in Section \ref{sec:websites}.
    The system has around $\approx 8,500$ indexed documents for searching, browsing and presented through a
    user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}, \ref{sec:ux}.

@@

    \subsection{Features}
    For this project, the following features have been implemented:
    \begin{itemize}
        \item Result presentation
        \item Filtering
        \item Automatic recommendation
    \end{itemize}

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{User Evaluation}
    System evaluation: Recall and precision paragraph
